### 2014-12-23 presentation/summer-slides.tex
Add slides for summer scholarship presentation

\begin{document}
\usydtitleframe{Data Mining Methods for Predicting Length of Hospital Stay}{}{\textbf{Tianyu Pu} Honours Student \\
  Supervisor: Irena Koprinska}

@@

\subsection{}
\begin{frame}{Outline of talk}
The problem

\vspace{0.5cm}
Background and previous work

\vspace{0.5cm}
Our approach

\vspace{0.5cm}
Results and discussion

\vspace{0.5cm}
Conclusions and future work
\end{frame}

@@

\subsection{}
\begin{frame}{Feature discretisation and selection}
\textbf{Discretisation}
\begin{itemize}
\item Convert numeric features into categorical features
\item \textit{Supervised} discretisation
\item Why?
\end{itemize}

@@

  \pause
\textbf{Selection}
\begin{itemize}
\item Find a subset of features that are the most `relevant'
\item Two ways: \textit{manual} and \textit{automatic}
\item Why?
\end{itemize}
\end{frame}

@@

\section{Approach}
\subsection{}
\begin{frame}{Proposed approach (1)}
Store all examples and do not try to generalise

Classify new example by looking at $k$ most `similar' (`nearest') examples
\begin{itemize}
\item \textit{Nearest neighbour} approach
\end{itemize}

\vspace{0.5cm}
\textbf{Similarity}

Typical approach: \textit{Euclidean distance}

\begin{equation*}
\sqrt{(x_1-y_1)^2 + (x_2-y_2)^2 + \ldots}
\end{equation*}
\end{frame}

\subsection{}
\begin{frame}{Proposed approach (2)}
Our approach: \textit{Ranked distance}
\begin{equation*}
w_1|x_1-y_1| + w_2|x_2-y_2| + \ldots
\end{equation*}

\vspace{0.5cm}
\textbf{Intuition}

The relative importance of a feature should determine its contribution to the similarity
\end{frame}

\subsection{}
\begin{frame}{Evaluation}
\textbf{Two datasets}: trauma and general hospital LOS data

\textbf{Procedure}:
\begin{enumerate}
\item Preprocess and discretise datasets $\implies$ 4 sets of data
\item Systematically evaluate 11 learning algorithms with 5 \textit{automatic} and 2 \textit{manual} feature selection methods
\end{enumerate}

  \pause
\textbf{Performance measures}: \textit{accuracy} and \textit{area under the curve (AUC)}
\end{frame}

\section{Results}
\subsection{}
\begin{frame}{Summary of best results}
\textbf{Trauma dataset}
\begin{center}
\begin{tabular}{l|cc}
 & Baseline & Our best result \\
\hline
Accuracy (\%) & 75.06 (19) & \textcolor{emerald}{77.81} (\textcolor{emerald}{11})\footnote{1-NN, C4.5 wrapper, discretised} \\
AUC & 0.812 (19) & \textcolor{emerald}{0.846} (\textcolor{sydneyred}{29})\footnote{Logistic regression, no feature selection, discretised} \\
\end{tabular}
\end{center}

\pause
\textbf{General hospital dataset}
\begin{center}
\begin{tabular}{l|c}
 & Our best result \\
\hline
Accuracy (\%) & 98.23 (14)\footnote{C4.5 decision tree, no feature selection or discretisation} \\
AUC & 0.994 (14)\footnote{Logistic regression, SVM and K*, no feature selection or discretisation} \\
\end{tabular}
\end{center}
\end{frame}

\subsection{}
\begin{frame}{Trauma data set}
\begin{center}
\includegraphics[width=0.93\textwidth]{tr-corr.eps}
\end{center}
\end{frame}

\subsection{}
\begin{frame}{General hospital data set}
\begin{center}
\includegraphics[width=0.92\textwidth]{pt-corr.eps}
\end{center}
\end{frame}

\subsection{}
\begin{frame}{Discussion}
Limitations of nearest neighbour methods

\vspace{0.5cm}
Trade-off between predictive power and number of features

\vspace{0.5cm}
Know your data!
\end{frame}

\section{Conclusions}
\subsection{}
\begin{frame}{Conclusions}
Comprehensive and systematic evaluation

\vspace{0.5cm}
Proposed new nearest neighbour algorithm

\vspace{0.5cm}
Improved accuracy by 2.75\% and AUC by 0.034 on the same dataset using nearest neighbour methods

\pause
\vspace{0.5cm}
\textbf{Future work}
\begin{itemize}
\item Ensembles
\item Different similarity measures
\item Implementation for doctors
\end{itemize}
\end{frame}

>>>>

\begin{document}
\usydtitleframe{Predicting the Length of Stay in Hospital Using Data Mining Methods}{}{\textbf{Tianyu Pu} \\
  Supervisors: Irena Koprinska \& Kalina Yacef}

@@

@@

\subsection{}
\begin{frame}{Feature discretisation and selection}
\textbf{Discretisation}
\begin{itemize}
\item Convert numeric features into categorical features
\item \textit{Supervised} discretisation
\end{itemize}

@@

  \pause
\textbf{Selection}
\begin{itemize}
\item Find a subset of features that are the most `relevant'
\item Two ways: \textit{manual} and \textit{automatic}
\end{itemize}
\end{frame}

@@

\subsection{}
\begin{frame}{Where We're At}
Comprehensive evaluation of feature selection, discretisation and learning algorithms
\pause

\vspace{0.5cm}
Proposed new nearest-neighbour approach
\end{frame}

\section{Next Steps}
\subsection{}
\begin{frame}{Next Steps}
Feedback from domain experts

\pause
\vspace{0.5cm}
Draft papers for publication
\pause

\vspace{0.5cm}
Investigate ensembles and refinement of nearest-neighbour method
\end{frame}
